Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-03-01 src/article.tex
Provide short description of CLI and API in results

>>>>

\subsection{Scaffolder Sofware Interface} %{{{2

Scaffolder provides a standardised set of Ruby classes and methods (API) for
interacting with the scaffold. This allows Scaffolder to be integrated into
existing genomics workflows or used with Ruby build tools such as Rake. In
addition Scaffolder provides a command line interface (CLI) providing functions
to validate the scaffold file and build a draft super sequence. This allows the
scaffold sequence to be generated and validated without any Ruby experience.
The Scaffolder CLI behaves as a standard Unix tool and returns appropriate exit
codes and manual pages. The use of both these Scaffolder interfaces is outlined
in detail on the scaffolder website (\scaffolder). \pb
